Learning action models with minimal observability

### 2018-11-23 doc/aij18/major-revision/letter.tex
added comments by reviewer2 with editor letter format

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Pages 9-13
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
  Pages 9-13
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
   Pages 9-13
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
   Pages 9-13
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
\end{mdframed}

>>>>

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
-          "On the other hand, a striking figure …" – I could not understand this sentence.

-          "Let $\Omega_v = {v_i}_{i=1}^{max_{a\in A} ar(a)}$ be a new set of objects …" – I think "ar(a)" should be "|ar(a)|"

-          "… which is bound to …" – I think should be " which is bounded by"

-          "In more details, for a given …" – delete the "In more details" as you are defining something new, not providing additional details.

-          Please elaborate on the computation of the size of the space of possible STRIPS models.

-          The definition of conditional effects given in 4.3 should be moved to the background section, where you define a STRIPS model.

-          The explanation about the plan prefix and postfix is confusing and not helpful. I recommend removing it. Only after you explain your solution it starts to make sense. Also, I am not sure the term "postfix" is suitable. Maybe "suffix"?

-          The formula for the precondition of apply uses the notation $\Rightarrow$ which was not defined.
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
Pages 15-19.

-          I'd appreciate more details on the mentioned post-processing, e.g., a pseudo code.

-          At the bottom of the page, you write that VAL cannot address the model validation of a partial model and on the other hand it requires a full plan and full action model. I don't see how this is "on the other hand"? it is the same "hand"

-          When introducing the semantic evaluation metrics, you provide two justification. One is that there is no GTM. The other is that a test-based evaluation is preferable. The latter justification is not really a justification. It is like saying "we justify using a test-based evaluation by the fact that test-based evaluation is sometimes preferred".

-          What does it mean that a learned action model is sound and complete?

-          "… to flaws that appear more than once in the plan traces …" – I recommend to clarify: "flaws in the action model that manifest more than once in the plan traces".

-          "… generated 10 plan traces (each with 10 actions …" – the parenthesis should be removed.

-          "… the horizon of the solution plan is also known. " – how do you know the horizon? You know the length of the given traces, but how do you know how many actions are needed to build the action model?

-          "… a solution plan is solvable in two steps" – which two steps? I thought you put it all in the planner and get both action model and validation in the same step.   
\end{mdframed}

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
   Pages 20-end of paper:

-          "… the size of the input knowledge, in the performance …" – should be "on the performance"

-          "… the Precision and Recall" – why capitalized?

-          "retain a level of soundness similar to " – what is this "level of soundness"? do you talk about precision?

-          "By lightening the input constraints …" – maybe "relaxing" instead of "lightening"?
\end{mdframed}
